Towards End-user Web Scraping For Customization

### 2021-02-16 paper.tex
add a note linking to the online version
Fix typo in section 3.4.2

@@

@@

Our currently system does not support scraping data loaded after the
initial websites render as the user scrolls. Site adapters hand-coded in
Javascript can specify event listeners on the DOM to re-execute the
scraping code when new data is loaded as a user scrolls. In future work,
we plan to provide a mechanism for end-users to specify when a
demonstrated adapter should re-execute its scraping code in response to
user scrolling. We also do not support scraping data across multiple
pages of related data, but this context poses more fundamental
challenges to the idea of web customization, since users would somehow
need to perform customizations across multiple pages in coordination.

>>>>

\usepackage{hyperref}

@@

This paper is directed at publication. We have provided a PDF but it is best viewed in the online version (\href{https://kapaya.github.io/px21/}{kapaya.github.io/px21}) which includes videos demonstrating the system.

@@

Our system currently does not support scraping data loaded after the
initial website renders as the user scrolls. Site adapters hand-coded in
Javascript can specify event listeners on the DOM to re-execute the
scraping code when new data is loaded as a user scrolls. In future work,
we plan to provide a mechanism for end-users to specify when a
demonstrated adapter should re-execute its scraping code in response to
user scrolling. We also do not support scraping data across multiple
pages of related data, but this context poses more fundamental
challenges to the idea of web customization, since users would somehow
need to perform customizations across multiple pages in coordination.
